Flat-histogram method comparison on the 2D Ising model

### 2020-06-23 ising/ising-body.tex
made minor changes; working on other paper now.

Nadler \emph{et al.} and Trebst \emph{et al.} systematically examined optimized
ensembles due to performance issues flat-histogram methods faced when
confronted with hidden energy barriers~\cite{nadler2007generalized,
nadler2007dynamics, trebst2004optimizing}. Trebst \emph{et al.} used their
optimized ensemble to systematically set the temperature range(s) and
implemented an optimized replica-exchange~\cite{trebst2006optimized}.
Replica-exchange Wang-Landau has been developed with great
success~\cite{perera2016magnetic} and adapting flat-histogram methods to use
such an optimized ensemble is doable

Last time for 32 X 32 is TL 2047388. Do I look at histogram to figure this out???

But optimized ensemble requires the energy range???

>>>>

% optimized ensemble paragraph
Nadler \emph{et al.} and Trebst \emph{et al.} systematically examined optimized
ensembles due to performance issues flat-histogram methods faced when
confronted with hidden energy barriers~\cite{nadler2007generalized,
nadler2007dynamics, trebst2004optimizing}. Trebst \emph{et al.} used their
optimized ensemble to systematically set the temperature range(s).

% replica exchange paragraph
Replica exchange Wang-Landau (REWL) was introduced~\cite{vogel2013rewl}.
Replica-exchange Wang-Landau has been developed with great
success~\cite{perera2016magnetic} and adapting flat-histogram methods to use
such an optimized ensemble is doable

% This goes in discussion section
Last time for 32 X 32 is TL 2047388. Do I look at histogram to figure this out??
But optimized ensemble requires the energy range???
Also, SAD doesn't appear to be impacted by the larger energy range? histogram counts outside the interesting energy range are negligible compared with count in the range of interest.
